Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-01 Paper/results.tex

%%%%%%%%%%% Compare Nalu/AMR TI/Temp profiles %%%%%%%%%%%%%%%%%%%%%%
% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
\begin{figure} %[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_TI.png}
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_T.png}
  \caption{\label{fig:CompareAMRvsNaluWind_TTI} Comparison of AMR-Wind
    and Nalu-Wind turbulence intensity and temperature profiles for
    the stable 5 m/s boundary layer. The dashed horizontal line
    corresponds to the measurement height z=20m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{ABL integrated quantities}
From the AMR-Wind calculations of the stable ABL at 5m/s, 10m/s, and
15m/s, a number of quantities can be computed to compare with the
measured targets from Archer et al \cite{archer2016predominance}.

The Obukhov length $L_{Ob}$ can be calculated as
\begin{equation}
  L_{Ob} = -\frac{u_\tau^3 T_0}{\kappa g \langle \overline{w'T'} \rangle}
\end{equation}
where the $\kappa$=0.41 is the Kolmogorov constant, $g$ is the
gravitational acceleration, and $\langle \overline{w'T'} \rangle$ is the
horizontally and time-averaged temperature flux.  In this study we use
the same classification guidelines as Archer et al
\cite{archer2016predominance}, and identify cases where $100 < L_{Ob}
< 500$ as ``stable'', and cases where $5 < L_{Ob}<100$ as ``very stable''.

%%%%%%%%%%%%%%% Compare AMR integrated quantities, all WS %%%%%%%%%%%%%%
% See Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{table}
\caption{\label{tab:CompareAMRallWS} Comparison of Stable ABL for all
  wind speeds} \centering
\begin{tabular}{ccccccc}
  \hline
  Code & Wind speed & TI      &  $\alpha$  &   $u_\tau$  &  Obukhov  $L_{Ob}$ & Stability \\
  \hline
  AMRWind & 5m/s      & 0.0483 &  0.166 &  0.157 m/s  &  52.5 m   & Very stable\\
  AMRWind & 10m/s     & 0.0506 &  0.160 &  0.319 m/s  &  57.2 m   & Very stable\\
  AMRWind & 15m/s     & 0.0550 &  0.118 &  0.511 m/s  & 131.3 m   & Stable \\
  \hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%% z=20m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/snapshots/05ms/velh_mag_z20.png}
  \includegraphics[width=2.5in]{figures/snapshots/05ms/velz_z20.png} \\

  \includegraphics[width=2.5in]{figures/snapshots/10ms/velh_mag_z20.png}
  \includegraphics[width=2.5in]{figures/snapshots/10ms/velz_z20.png} \\

  \includegraphics[width=2.5in]{figures/snapshots/15ms/velh_mag_z20.png}
  \includegraphics[width=2.5in]{figures/snapshots/15ms/velz_z20.png} \\
  \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
    velocity and vertical velocity }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% side snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[height=2.0in]{figures/snapshots/05ms/velh_mag_side.png} \\

  \includegraphics[height=2.0in]{figures/snapshots/10ms/velh_mag_side.png} \\

  \includegraphics[height=2.0in]{figures/snapshots/15ms/velh_mag_side.png} \\

  \caption{ \label{fig:SnapshotsSide} Snapshots of the horizontal
    velocity and vertical velocity }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \label{fig:CompareAMRallWS}
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WS.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WDir.png}
  \caption{Comparison of the horizontal wind speed and wind direction
    profile for the stable 5m/s, 10m/s, and 15m/s boundary layers. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \label{fig:CompareAMRallTTI}
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_TI.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_T.png}
  \caption{Comparison of the turbulence intensity and temperature
    profile for the stable 5m/s, 10m/s, and 15m/s boundary layers. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{Wind spectra and turbulence statistics}

The Kaimal model for spectra \cite{kaimal1973turbulence,
  cheynet2017spectral} for neutral atmospheric conditions:
\begin{equation}
  \label{eq:kaimal}
  \frac{fS_i}{u_\tau^2} = \frac{a_i(fz/\bar{U})}{\left(1+b_i(fz/\bar{U})^{\alpha_i}\right)^{\beta_i}}
\end{equation}

%%%%%%%%%%%%%%% KAIMAL MODEL PARAMETERS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
\caption{\label{tab:KaimalParameters} Parameters for Kaimal model}
\centering
\begin{tabular}{ccccc}
  \hline
  Index $i$& $a_i$ & $b_i$ & $\alpha_i$  & $\beta_i$ \\
  \hline
  $u$      & 105.0 & 33.0  & 1           & 5/3  \\
  $v$      &  17.0 &  9.5  & 1           & 5/3  \\
  $w$      &   2.1 &  5.3  & 5/3         &   1  \\
\hline
\end{tabular}
\end{table}

%%%%%%%%%%% Stable spectra, all Z figure %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLSpectra/Stable_Spectra_Allz.ipynb
\begin{figure}[hbt!]
  \label{fig:ABLSpectra_AllZ}
  \centering
  \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_05ms.png}\\
  \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_10ms.png}\\
  \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_15ms.png}
  \caption{Calculation of the wind spectra $S_i$ for LES of stable
    5m/s, 10m/s, and 15m/s cases at z=20m, 40m, and 60m.  The black
    vertical lines correspond to the maximum resolvable frequency
    $f_{max}$ according to equation (\ref{eq:fmax}). }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%% All stability correlation figure %%%%%%%%%%%%%%%%%%%%
% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
\begin{figure}[hbt!]
  \label{fig:AllStabilityRij}
  \centering
  \includegraphics[width=3in]{figures/AllStability_Rij_Longitudinal.png}
  \includegraphics[width=3in]{figures/AllStability_Rij_Lateral.png}
  \caption{Calculation of the averaged longitudinal and lateral
    $R_{11}(\xi)$ coefficient at $z$=20m for all ABL stability cases.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% All stability, turbulent L figure %%%%%%%%%%%%%%%%%%%%
% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
\begin{figure}[hbt!]
  \label{fig:AllStabilityLengthscale}
  \centering
  \includegraphics[width=3in]{figures/AllStability_Rij_LongitudinalLengthscale.png}
  \includegraphics[width=3in]{figures/AllStability_Rij_LateralLengthscale.png}
  \caption{Calculation of the averaged longitudinal and lateral
    lengthscale at $z$=20m for all ABL stability cases.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%% Compare Nalu/AMR TI/Temp profiles %%%%%%%%%%%%%%%%%%%%%%
% Postprocessing/ABLStats/AMRWind_NaluWind_stable_05ms_mesh2_5x2_5x2_5_paper.ipynb
\begin{figure} [hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_TI.png}
  \includegraphics[width=2.5in]{figures/Compare_AMRWind_NaluWind/AMRWind_NaluWind_stable_05ms_mesh2p5_2p5_2p5_T.png}
  \caption{\label{fig:CompareAMRvsNaluWind_TTI} Comparison of AMR-Wind
    and Nalu-Wind turbulence intensity and temperature profiles for
    the stable 5 m/s boundary layer. The dashed horizontal line
    corresponds to the measurement height z=20m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{\label{sec:stableABLStats} ABL integrated quantities}
From the AMR-Wind calculations of the stable ABL at 5m/s, 10m/s, and
15m/s, a number of quantities can be computed to compare with the
measured targets from Archer et al \cite{archer2016predominance}.  In
table \ref{tab:CompareAMRallWS}, we list the TI, shear exponent
$\alpha$, friction velocity $u_\tau$, Obukhov length $L_{Ob}$,
longitudinal lengthscale $L$, and stability classification for each of
these three cases.  The TI values, calculated at the height $z$=20m
fall within the target range of 4.5\% to 6.0\% for stable conditions
from the Cape Wind measurements.  The calculated friction velocities
are also similar to the values from the neutral offshore ABL
calculations of \cite{cheung2020large}, where $u_\tau$ varied from
0.15 m/s to 0.51 m/s for wind speeds of 5 m/s to 15 m/s.

The degree of stratification in each of the marine boundary layers can
be quantified through the Obukhov length $L_{Ob}$, defined here as 
\begin{equation}
  L_{Ob} = -\frac{u_\tau^3 T_0}{\kappa g \langle \overline{w'T'} \rangle}
\end{equation}
where the $\kappa$=0.41 is the Kolmogorov constant, $g$ is the
gravitational acceleration, $T_0$ is the reference temperature, and
$\langle \overline{w'T'} \rangle$ is the horizontally and
time-averaged temperature flux.  In this study we adopt the same
classification guidelines as Archer et al
\cite{archer2016predominance}, and identify boundary layer cases where
$100 < L_{Ob} < 500$ as ``stable'', and cases where $5 < L_{Ob}<100$
as ``very stable''.  From the values listed in table
\ref{tab:CompareAMRallWS}, we find that the lower wind speeds are
``very stable'', while the highest 15 m/s wind speed is classified as
``stable''.  This is consistent with the measured Cape Wind
distributions, where very stable conditions are more frequent than
stable conditions at lower wind speeds, and gradually disappear beyond
13 m/s (c.f. figure 5b in \cite{archer2016predominance}).

%%%%%%%%%%%%%%% Compare AMR integrated quantities, all WS %%%%%%%%%%%%%%
% See Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{table}
\caption{\label{tab:CompareAMRallWS} Comparison of Stable ABL for all
  wind speeds} \centering
\begin{tabular}{cccccccc}
  \hline
  Code & Wind speed   & TI     & $\alpha$& $u_\tau$ & Obukhov $L_{Ob}$ & Longitudinal $L$ & Stability \\
  \hline
  AMRWind & 5m/s      & 0.0483 &  0.166 &  0.157 m/s  &  52.5 m & 27.7 m  & Very stable\\
  AMRWind & 10m/s     & 0.0506 &  0.160 &  0.319 m/s  &  57.2 m & 29.6 m  & Very stable\\
  AMRWind & 15m/s     & 0.0550 &  0.118 &  0.511 m/s  & 131.3 m & 43.8 m  & Stable \\
  \hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The qualitative behavior of the stable boundary layers can be seen
through snapshots of the flow taken from each of the simulations.  In
figure \ref{fig:SnapshotsZ20}, instantaneous snapshots of the
horizontal and vertical velocities for each of the three cases at the
z=20m measurement height are shown.  The largest difference can be
seen in the size of the flow structures between the very unstable and
stable cases.  Longer streaks are evident in the 15 m/s case compared
to the 5 m/s and 15 m/s cases, which is consistent with the nearly
50\% larger integral lengthscale $L$ given in table
\ref{tab:CompareAMRallWS}.  The differences in the vertical velocity
are also evident in \ref{fig:SnapshotsZ20}.  At higher wind speeds the
magnitude of the vertical $w'$ fluctuations increase, which plays a
strong role in the growth the boundary layer.

%%%%%%%%%%% z=20m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velz_z20.png} \\

  \includegraphics[width=3.0in]{figures/snapshots/10ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/10ms/velz_z20.png} \\

  \includegraphics[width=3.0in]{figures/snapshots/15ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/15ms/velz_z20.png} \\
  \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
    velocity and vertical velocity, taken at t=20,000 seconds of the
    simulations at height z=20m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This observation can also be seen in images taken along the flow
direction $\theta=225^\circ$, as shown in figure
\ref{fig:SnapshotsSide}.  At the time t=20,000 seconds, the growth the
of 15 m/s stable boundary layer is considerably larger than the very
stable 5 m/s and 10 m/s cases, and has nearly reached the inversion
layer height.  To reach the same level of boundary layer growth, the
very stable ABL cases would require longer simulation times, possibly
longer than the nighttime conditions measured experimentally.

%%%%%%%%%%% side snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
  \includegraphics[height=2.5in]{figures/snapshots/05ms/velh_mag_side.png} \\

  \includegraphics[height=2.5in]{figures/snapshots/10ms/velh_mag_side.png} \\

  \includegraphics[height=2.5in]{figures/snapshots/15ms/velh_mag_side.png} \\

  \caption{ \label{fig:SnapshotsSide} Snapshots of the horizontal
    velocity, taken at t=20,000 seconds along the wind direction. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Horizontally averaged flow profiles shown in figures
\ref{fig:CompareAMRallWS} and \ref{fig:CompareAMRallTTI} provide a
more quantitative assessment of the ABL evolution.  The rapid growth
of the 15 m/s stable case leads to strong shear throughout the
boundary layer up to the inversion height, while the very stable 5 m/s
and 10 m/s cases showed minimal shear at higher elevations.  The
change in wind direction is also indicative of the boundary layer
penetration.  Approximately linear veer profiles are visible up to
heights of $z\approx$250 m and $z\approx$350 m for the 5 m/s and 10
m/s cases, respectively, while the linear veer is present in the 15
m/s stable case up to $z$=650m.

The behavior of the TI and temperature profiles in figure
\ref{fig:CompareAMRallTTI} closely follows the shear and veer profiles
discussed above.  Despite all cases reaching a similar TI levels at
$z$=20m, the turbulence decays at different rates for each case until
reaching the top of the boundary layer.  The effect of the different
surface temperature changes is also visible in the horizontally
averaged temperature profiles.  Both the 10 m/s and 15 m/s impose
similar temperature changes (-1.4 K/hr and -1.5 K/hr, respectively)
and each similar temperatures at the ocean surface.  However, the
cooling effect in the very unstable 10 m/s case is limited to $z$<350
m, similar to the veer and turbulence profiles.

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WS.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_WDir.png}
  \caption{ \label{fig:CompareAMRallWS} Comparison of the horizontal
    wind speed and wind direction profile for the stable 5m/s, 10m/s,
    and 15m/s boundary layers. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% stable WS profiles %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_TI.png}
  \includegraphics[width=2.5in]{figures/AMRWind_allWS/AMRWind_stable_T.png}
  \caption{ \label{fig:CompareAMRallTTI} Comparison of the turbulence
    intensity and temperature profile for the stable 5m/s, 10m/s, and
    15m/s boundary layers. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% \subsubsection{Wind spectra and turbulence statistics}

%% The Kaimal model for spectra \cite{kaimal1973turbulence,
%%   cheynet2017spectral} for neutral atmospheric conditions:
%% \begin{equation}
%%   \label{eq:kaimal}
%%   \frac{fS_i}{u_\tau^2} = \frac{a_i(fz/\bar{U})}{\left(1+b_i(fz/\bar{U})^{\alpha_i}\right)^{\beta_i}}
%% \end{equation}

%% %%%%%%%%%%%%%%% KAIMAL MODEL PARAMETERS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \begin{table}[h]
%% \caption{\label{tab:KaimalParameters} Parameters for Kaimal model}
%% \centering
%% \begin{tabular}{ccccc}
%%   \hline
%%   Index $i$& $a_i$ & $b_i$ & $\alpha_i$  & $\beta_i$ \\
%%   \hline
%%   $u$      & 105.0 & 33.0  & 1           & 5/3  \\
%%   $v$      &  17.0 &  9.5  & 1           & 5/3  \\
%%   $w$      &   2.1 &  5.3  & 5/3         &   1  \\
%% \hline
%% \end{tabular}
%% \end{table}

%% %%%%%%%%%%% Stable spectra, all Z figure %%%%%%%%%%%%%%%%%%%%%%%%%
%% % Created in Postprocessing/ABLSpectra/Stable_Spectra_Allz.ipynb
%% \begin{figure}[hbt!]
%%   \label{fig:ABLSpectra_AllZ}
%%   \centering
%%   \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_05ms.png}\\
%%   \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_10ms.png}\\
%%   \includegraphics[width=7.0in]{figures/Stable_Spectra_AllZ_15ms.png}
%%   \caption{Calculation of the wind spectra $S_i$ for LES of stable
%%     5m/s, 10m/s, and 15m/s cases at z=20m, 40m, and 60m.  The black
%%     vertical lines correspond to the maximum resolvable frequency
%%     $f_{max}$ according to equation (\ref{eq:fmax}). }
%% \end{figure}
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Strong differences based on the atmospheric stratification can also be
seen when we compare the stable ABL cases with the neutral and
unstable counterparts from \cite{cheung2020large}.  In the previous
study, both neutral and unstable offshore boundary layer cases were
considered at the same 5 m/s, 10 m/s and 15 m/s wind speeds.  Similar
to the findings in \ref{sec:stableABLStats}, the 5 m/s and 10 m/s
unstable cases were classified as ``very unstable'', while the 15 m/s
was identified as ``stable'' based on the Obukhov length scale.

The impact of the stability on the turbulent structures can be seen
through the correlation statistics and calculated lengthscales in
figure \ref{fig:AllStabilityRij} and
\ref{fig:AllStabilityLengthscale}.  The large disparity between the
size of the turbulent structures in the stable and neutral or unstable
cases is immediately evident from the calculated $\langle
R_{11}(\boldsymbol{\xi})\rangle$ coefficients.  The longitudinal
lengthscales for the unstable ABL cases can also be an order of
magnitude larger than the stable ABL cases.  The large lateral
lengthscales for the very unstable ABL cases, compared to the lateral
lengthscales for the neutral and stable cases, is also worth noting.
For the 5 m/s and 10 m/s very unstable ABL cases, the lateral
dimensions of the turbulent structures are similar to the longitudinal
lengthscale.  This is consistent with the large convective structures
which develops in those cases.  For the unstable 15 m/s case, the
lateral lengthscales was closer to neutral and stable cases.

%%%%%%%%%%% All stability correlation figure %%%%%%%%%%%%%%%%%%%%
% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
\begin{figure}[hbt!]
  \centering
  \fxnote{Fix legend and line styles} \\
  \includegraphics[width=3in]{figures/AllStability_Rij_Longitudinal.png}
  \includegraphics[width=3in]{figures/AllStability_Rij_Lateral.png}
  \caption{ \label{fig:AllStabilityRij} Calculation of the averaged
    longitudinal and lateral $R_{11}(\xi)$ coefficient at $z$=20m for
    all ABL stability cases.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%% All stability, turbulent L figure %%%%%%%%%%%%%%%%%%%%
% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
\begin{figure}[hbt!]
  \centering
  \fxnote{Fix legend and marker styles} \\
  \includegraphics[width=3in]{figures/AllStability_Rij_LongitudinalLengthscale.png}
  \includegraphics[width=3in]{figures/AllStability_Rij_LateralLengthscale.png}
  \caption{ \label{fig:AllStabilityLengthscale} Calculation of the
    averaged longitudinal and lateral lengthscale at $z$=20m for all
    ABL stability cases.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
